A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-02-18 src/tex/ms.tex
Manuscript updates

% Author list
\author[0000-0003-3781-0747]{Liam O.\ Dubay}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0001-7258-1834]{Jennifer A.\ Johnson}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0002-6534-8783]{James W.\ Johnson}
\affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
% \author[0000-0001-7775-7261]{David H. Weinberg}
\author{coauthors}

@@

Our second age catalog uses the [C/N]--age relation for red giant branch and red clump stars. 
\todo{Paragraph describing [C/N]-derived ages (get help from Jack).}
This method has the benefit of providing age estimates for luminous giants, which increases the sample size at farther distances from the Sun. However, systematic effects of the [C/N]--age relation mean that these ages are most trustworthy in the range $1\sim10$ Gyr.

@@

\begin{itemize}
    \item
\end{itemize}

>>>>

% Author list
\author[0000-0003-3781-0747]{Liam O.\ Dubay}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0001-7258-1834]{Jennifer A.\ Johnson}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0002-6534-8783]{James W.\ Johnson}
\affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0002-2854-5796]{John D. Roberts}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
% \author[0000-0001-7775-7261]{David H. Weinberg}
\author{coauthors}

@@

Our second age catalog uses the [C/N]--age relation for red giant branch and red clump stars. 
\todo{Paragraph describing [C/N]-derived ages (get help from Jack).}
This method has the benefit of providing age estimates for luminous giants, which increases the sample size at farther distances from the Sun. However, systematic effects of the [C/N]--age relation mean that these ages are most trustworthy in the range $1\sim10$ Gyr. We estimate ages for \num{113464} stars across the disk, including \num{20995} in the Solar neighborhood.

@@

\begin{itemize}
    \item The ``turn-over'' in the evolution of [O/Fe] following the second infall produces a low-$\alpha$ sequence with a fundamentally different abundance structure than observed. A low yield set ($y/Z_\odot=1$) coupled with lower outflows, or pre-enrichment of the infalling gas, can bring the stellar [O/Fe] distributions more in line with the data.
    \item The large quantity of pristine gas accreted in the Solar neighborhood during the second infall phase rapidly dilutes the ISM metallicity by $\sim0.5$ dex. Models with a low yield set ($y/Z_\odot=1$) remain at sub-Solar metallicity until the present day, in stark contrast to the observed local age--metallicity relation. This issue can be mitigated with higher yields and outflows, but not by pre-enriched infall or radial migration.
    \item Our models predict that the MDF evolves to higher metallicity over time throughout the disk. This contrasts with the APOGEE data, which show very little change in the mode over the past $\sim6-8$ Gyr.
\end{itemize}
